---
title: "Marketing Report"
subtitle: "Office of Marketing and Brand Management"
date: "`r Sys.Date()`"
output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: default
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tufte)
library(ggplot2)
library(formatR)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(
	echo = FALSE,
	cache.extra = packageVersion("tufte"),
	tidy = FALSE
)
options(htmltools.dir.version = FALSE)
```

# Description


`r newthought('Intro text here')` Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here. In general,
    \href{https://blog.adstage.io/facebook-ads-benchmarks}{{\color{blue}{\underline{FB Newsfeed }}}} CTR overall experienced a 24% drop from July, 2017 - July, 2018.



# Findings

## Plots



```{r fig-fullwidth, echo=FALSE, fig.cap="This is a full width plot.", fig.fullwidth=TRUE, fig.height=2, fig.width=10, message=FALSE, cache=TRUE}

#代码段选项`fig.fullwidth = TRUE`可以使得一幅图占用全部页宽，例如：
ggplot(diamonds, aes(carat, price)) + geom_smooth() +
  facet_grid(~ cut)
```

## Margin Figures

Images and graphics play an integral role in Tufte's work. To place figures in the margin you can use the **knitr** chunk option `fig.margin = TRUE`. For example:

```{r fig-margin, fig.margin = TRUE, fig.cap = "MPG vs horsepower, colored by transmission.", fig.width=3.5, fig.height=3.5, cache=TRUE, message=FALSE}

mtcars2 <- mtcars
mtcars2$am <- factor(
  mtcars$am, labels = c('automatic', 'manual')
)
ggplot(mtcars2, aes(hp, mpg, color = am)) +
  geom_point() + geom_smooth() +
  theme(legend.position = 'bottom')
```



## Sidenotes



If you'd like to place ancillary information in the margin without the sidenote mark (the superscript number), you can use the `margin_note()` function from **tufte** in an inline R expression. `r margin_note("This is a margin note.  Notice that there is no number preceding the note.")` This function does not process the text with Pandoc, so Markdown syntax will not work here. If you need to write anything in Markdown syntax, please use the `marginfigure` block described previously.





## Tables

You can use the `kable()` function from the **knitr** package to format tables that integrate well with the rest of the Tufte handout style. The table captions are placed in the margin like figures in the HTML output.

Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here.
Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here.
Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here.




```{r}
knitr::kable(
  mtcars[1:6, 1:6], caption = 'A subset of mtcars.'
)
```


```{marginfigure, echo = TRUE}
Notice that there is no number preceding the note. $x \in [a, b]$有
$$\frac{d}{dx}\left( \int_{a}^{x} f(u)\,du\right)=f(x).$$
```

## Plots with Margin Notes

Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here.
If you'd like to place ancillary information in the margin without the sidenote mark (the superscript number), you can use the `margin_note()` function from **tufte** in an inline R expression. 



```{r fig-main, fig.cap = "Some general comments about this plot. $500 Notice the dollar sign renders.", cache=TRUE, echo = TRUE}
ggplot(diamonds, aes(cut, price)) + geom_boxplot()
```


```{marginfigure, echo = TRUE}
Notice that there is no number preceding the note. $x \in [a, b]$有
$$\frac{d}{dx}\left( \int_{a}^{x} f(u)\,du\right)=f(x).$$
```

# ROI

Profit Profit Profit
Profit Profit Profit
Profit Profit Profit

# Conclusion

* 代码段选项
* 代码段选项
* 代码段选项

```{r bib, include=FALSE}
# create a bib file for the R packages used in this document
knitr::write_bib(c('base', 'rmarkdown'), file = 'skeleton.bib')
```
