---
title: "FY20 Search Names Purchased"
subtitle: "Office of Marketing and Brand Management"
date: "`r Sys.Date()`"

output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: default
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: tinytex
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tufte)
library(knitr)
library(formatR)
library(blastula)
library(gt)
library(glue)
library(formattable)
library(hms)
library(tidyverse)
library(knitr)
library(ggpubr)
library(treemapify)
library(treemap)


# invalidate cache when the tufte version changes
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	cache.extra = packageVersion("tufte"),
	tidy = FALSE
)
options(tinytex.verbose = TRUE)
```

```{r, include=FALSE}
#source("C:/Users/christine.iyer/Box/FY20_Advertising__FilterTableByVendor/DataTidyingForAds.R")
```

# __Office of Marketing and Brand Management__

# Description


`r newthought('The purpose of this document')` is to summarise the FY20 Lead Names Purchased. 

* There were 3 search campaigns. 

* There were 4 actual search name purchase transactions. 

* We purchased SR, JR, and PH names from the College Board for which we have P.O. numbers.

* As part of the annual NRCCUA contract, which costs `$27,700.00`, we prepay for 45,000 names at `$0.47`, bringing the annual cost for search names to `$21,150.00`.






# Findings

```{r}
NRC1 <- read.csv("C:/Users/christine.iyer/Downloads/NRC1.csv", header = T, stringsAsFactors = F)
NRC2 <- read.csv("C:/Users/christine.iyer/Downloads/NRC2.csv", header = T, stringsAsFactors = F)
NRC3 <- read.csv("C:/Users/christine.iyer/Downloads/NRC3.csv", header = T, stringsAsFactors = F)
NRCCUA <- rbind.data.frame(NRC1, NRC2, NRC3)
```

__NRCCUA Leads__


```{marginfigure, echo = TRUE}
Note: PH = Sophomore
```

```{r}
kable(NRCCUA %>% group_by(Graduation.Year) %>%
  
  summarise(`Lead Names Purchased` = n()) %>% 
  mutate(
    Class = ifelse(Graduation.Year == 2020, "SR", 
                   ifelse(Graduation.Year == 2021, "JR", "PH")), 
    Cost = paste0("$",prettyNum(`Lead Names Purchased`*0.47, big.mark = ",")), 
    `Lead Names Purchased` = prettyNum(`Lead Names Purchased`, big.mark = ",")) %>% 
  select(Class, `Lead Names Purchased`, Cost))
```

__College Board Leads__

```{r}
Class <- c("SR", "JR", "PH")
`Lead Names Purchased` <- c("8,236", "66,258", "21,975")
Cost <- c("$3,870.92", "$31,141.26", "$10,328.25")
CB <- data.frame(Class, `Lead Names Purchased`, Cost)
kable(CB)
  
```


```{r eval=FALSE, include=FALSE}
image <- "C:/Users/christine.iyer/Pictures/FY20_Search.PNG"


imgur_image <-
   add_imgur_image(
     image = image,
     client_id = "851117406f0b457"
   )
#Email

# The plot to the side will be included in an email. 




body_text <-
  glue(
    "


Hi Tracy, \\
Attached is a  \\
because the census report is a couple months away. We \\
discussed criteria for a new list which will hopefully \\ 
include students who have deposited and are due to start \\
in the upcoming months. This will give us a second year \\
of applications so we can look at the patterns of ap-\\
plication flow. He's sending the list by EOD tomorrow.



{imgur_image}


Thank you,

Christine Iyer \\
Marketing Data Analyst \\
University of Southern Maine
"
  ) %>% md()

compose_email(body = body_text) %>%
  smtp_send(
    #to = "wrike+into523544264@wrike.com",
    to = "edithbird5@gmail.com",
    #cc = "tracy.st@maine.edu",
    from = "christine.iyer@maine.edu",
    subject = "Project Update",
    credentials = creds_key(id = "gmail")
  )
```


__Breakdown of All FY20 Purchased Leads by Class__

```{r}
Class <- c("SR", "JR", "PH")
Leads_Purchased <- c(17869, 93120, 30480)

Cost <- c(8398.43, 43766.40, 14325.60)
NothData <- data.frame(Class, Leads_Purchased, Cost)
NothData <- 
  NothData %>%  
        mutate( 
          Cost_USD = paste0("$",prettyNum(Cost, big.mark = ",")),
          Leads = prettyNum(Leads_Purchased, big.mark = ","),
          Percent_of_Whole = paste0(round(Leads_Purchased/sum(Leads_Purchased) *100,0), "%"), 
          Percent = Leads_Purchased/sum(Leads_Purchased)) 
kable(NothData %>% 
  select(Class, Leads, Cost_USD, Percent_of_Whole))

```



```{r fig.height=1.5, fig.width=2}
colorsP <-  c("#F6A704", "#0E1033","#4E7B14","#A92007","#D47E0A")
NothData$label <- paste(NothData$Class, NothData$Percent_of_Whole, sep = " ")
treemap(NothData,index = "label",vSize = "Leads_Purchased",title = "FY20 Lead Names: Class Breakdown",
    fontsize.title=5,palette = colorsP)
```



# Conclusions

 
* We spent a total of `$45,340.43` for CB names. 

* The NRCCUA names, included in annual contract, would cost `$21,150.00`

* In FY20 we spent a total of `$66,490.43` on lead names alone. 




__For Reference: College Board Individual Purchases__



| Class | Month|Leads|Cost|P.O. Number|Chart Fields|
|-------|-------|--------|--------|-----------------|----------|
|SR|NOV|3,354|$1576.38|PO #: 6100526728|Admissions|
|JR|NOV|14,399|$6,767.53|PO #: 6100526729|Admissions|
|SR|JAN_1|4,882|$2,294.54|PO #: 6100538943|Admissions|
|JR|JAN_1|16,393|$7,704.71|PO #: 6100538936|Admissions|
|JR|JAN_2|29,557|$13,891.79|PO #: 6100542417|Enrollment|
|PH|JAN_2|17,252|$8,108.44|PO #: 6100542289|Enrollment|
|JR|APR|5,909|$2,777.23|PO #: 6100546475|Admissions|
|PH|APR|4,723|$2,219.81|PO #: 6100546474|Admissions|



\href{https://www.wrike.com/open.htm?id=532465819}{{\color{blue}{\underline{Wrike Project Details}}}}

\href{https://github.com/edithbird/search-general-information}{{\color{blue}{\underline{Github Repository}}}}






```{r bib, include=FALSE}
# create a bib file for the R packages used in this document
knitr::write_bib(c('base', 'rmarkdown'), file = 'skeleton.bib')
```
