---
title: "Your Document Title"
author: "Document Author"
date: "`r Sys.Date()`"
output:
  
  prettydoc::html_pretty:
    theme: cayman 
    highlight: github
---

## A New Output Format

`html_pretty` in the [**prettydoc**](https://github.com/yixuan/prettydoc/)
package is a new output format for creating HTML documents from R Markdown files.
`html_pretty` is more lightweight compared to `html_document`, and is more
stylish than `html_vignette` when creating package vignettes.

## New Styles

`html_pretty` currently supports three page themes (`cayman`, `tactile` and
`architect`), and two syntax highlight styles (`github` and `vignette`).
The theme and highlight styles can be specified in the document metadata,
for example:

```yaml
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
```

## Your Familiar Tools

Feel free to use the `knitr` infrastructure with dozens of tunable options in
your document.

```{r}
library(dplyr)
library(ggplot2)
dates <- read.csv("/Users/christine.iyer/Box/Search/Search General Information/SearchPurchaseDates.csv", header = T, stringsAsFactors = F)
dates <- dates %>% group_by(Date = as.Date(Created.Date, format = "%m/%d/%Y")
#                            , Country = Primary.Country
                            ) %>%
  summarise(n = n()) %>% 
  filter(
    #Date > "2016-06-30", 
         n>100
         )
range(dates$Date)
dim(dates)
dates
write.csv(dates, "/Users/christine.iyer/Box/Search/Search General Information/Dates.csv", row.names = F)

dates <- read.csv("/Users/christine.iyer/Box/Search/Search General Information/Dates.csv", header = T, stringsAsFactors = F)
dates <- dates %>% rename(Leads = n)
```


```{r fig.width=6, fig.height=6, fig.align='center'}

ggplot(dates, aes(x = Date)) + 
geom_bar(fill = "blue", alpha = 0.5) + 
theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
geom_boxplot(data = dates, aes(x = Date, y = Leads, fatten = 4)) + 
labs(title = "Purchase Dates", subtitle = "Historical Leads") +
labs(x="Date",y="Total Number of Leads in SF")
```

You can include code snippets of languages other than R, but note that
the block header has no curly brackets around the language name.

```cpp
// [[Rcpp::export]]
NumericVector timesTwo(NumericVector x) {
    return x * 2;
}
```

You can also write math expressions, e.g. $Y = X\beta + \epsilon$,
footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(dates)
```

## Stay Tuned

Please visit the [development page](https://github.com/yixuan/prettydoc/) of the 
`prettydoc` package for latest updates and news. Comments, bug reports and
pull requests are always welcome.


```{r}

ggplot(iris, aes(x = Species)) + 
geom_bar(fill = "blue", alpha = 0.5) + 
theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
geom_boxplot(data = iris, aes(x = Species, y = Sepal.Width, fatten = 4)) + 
labs(title = "All Trips", subtitle = "Black line demarcates the number of trips to Russia") +
labs(x="Government Official",y="Total Number of Trips")
```

