---
title: "FY21 NRCCUA Declared Students"
subtitle: "Availability as of June 17, 2020"
author: "Office of Marketing and Brand Management"
address: "University of Southern Maine"     
logo: C:/Users/christine.iyer/Downloads/blueLogo.png
date: '`r format(Sys.Date(), "%B %d, %Y")`' 
fontfamily: lmodern
fontsize: 12pt
graphics: null
papersize: 
geometry: margin=1.0in
classoption:
  - oneside
  #- more options here, see rmarkdown documentation 
UP_title: yes
UP_subtitle: yes
shaded_quote: yes
output: 
  yart::yart
---



```{r setup, include=FALSE, echo = FALSE, warning = FALSE, fig.align="center"}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```


```{r}
library(tidyverse)
library(knitr)
library(googlesheets4)
```

```{r}
data_NR <- read.csv("C:/Users/christine.iyer/Box/Search/Search General Information/NRCCUA Stuff/NRCCUADeclared.csv", header = T)
data_NR <- data_NR %>% select(Start,State, Number)
```

# Basic Description

The datalab.encoura website offers an abundance of information pertinent to Higher Education Search. In addition to providing research findings on national trends in enrollment, student mindsets, and student sentiment, it should also be used as a tool for the University of Southern Maine (USM) to check availability and quantity of lead and inquiry names with filters for location, class, and rank. 

Per our annual contract, USM has prepaid for 45,000 lead names. Orders can be placed for prospective student search (leads) on this website or through our representative. In addition, the availability of declared students can be researched there. A __Declared Student__, according to the description on the website, is one who has "expressed unaided and specific interest in attending [our] institution in particular." The cohort is much smaller; however, NRCCUA purports these students are, on average, 8 times more likely to enroll here when compared to other inquiries. As a result the cost for these inquiries is much higher at $12.00 each. 

This document reflects the number of declared students available as of June 17, 2020 with ANY self-declared GPA. I have selected only states where we most actively recruit.



---

# Findings

### Rising Seniors

```{r echo=FALSE}
data_NR_SR <- data_NR %>% filter(Start == "Fall 2021")  
kable(data_NR_SR %>% arrange(desc(Number)))
```

### Rising Juniors

```{r echo=FALSE}
data_NR_JR <- data_NR %>% filter(Start == "Fall 2022")  


kable(data_NR_JR%>% arrange(desc(Number)))
```

### Rising Sophomores

```{r echo=FALSE}
data_NR_PH <- data_NR %>% filter(Start == "Fall 2023")  

kable(data_NR_PH%>% arrange(desc(Number)))
```

---

# Conclusions 

* The total cost for all 315 declared students would be $3,780.00.

* Cost for all 178 declared rising Seniors would be $2,136.00

* Cost for all 108 declared rising Seniors would be $1,296.00

* Cost for all 29 declared rising Seniors would be $348.00

* If we select only the 302 students with a GPA of C+ or higher, the total cost would drop by $156.00

* It is important to understand that many of the Declared Students will already be in our database because we will have acquired them as leads (as long as we purchase from their county).
If leads have not converted to inquiries through one of our referral channels, 
we will not know they bacame inquiries unless we pay the declared student rate. The purchase of declared students will likely only be justified if they are pursued by the Office of Admissions.  

