---
title: "FY21 NRCCUA Declared Students"
subtitle: "Availability as of June 17, 2020"
author: "Office of Marketing and Brand Management"
address: "University of Southern Maine"     
logo: C:/Users/christine.iyer/Downloads/blueLogo.png
date: '`r format(Sys.Date(), "%B %d, %Y")`' 
fontfamily: lmodern
fontsize: 12pt
graphics: null
papersize: 
geometry: margin=1.0in
classoption:
  - oneside
  #- more options here, see rmarkdown documentation 
UP_title: yes
UP_subtitle: yes
shaded_quote: yes
output: 
  yart::yart
---



```{r setup, include=FALSE, echo = FALSE, warning = FALSE, fig.align="center"}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```


```{r}
library(tidyverse)
library(knitr)
library(googlesheets4)
```

```{r}
data_NR <- read.csv("C:/Users/christine.iyer/Box/Search/Search General Information/NRCCUA Stuff/NRCCUADeclared.csv", header = T)
data_NR <- data_NR %>% select(Start,State, Number)
```

# Basic Description

The datalab.encoura website offers an abundance of information pertinent to Higher Education Search. In addition to providing research findings on national trends in enrollment, student mindsets, and student sentiment, it should also be used as a tool for the University of Southern Maine (USM) to check availability and quantity of lead and inquiry names with filters for location, class, and rank. 

Per our annual contract, USM has prepaid for 45,000 lead names. Orders can be placed for prospective student search (leads) on this website or through our representative. In addition, the availability of declared students can be researched there. A __Declared Student__, according to the description on the website, is one who has "expressed unaided and specific interest in attending [our] institution in particular." The cohort is much smaller; however, NRCCUA purports these students are, on average, 8 times more likely to enroll here when compared to other inquiries. As a result the cost for these inquiries is much higher at $12.00 each. 

This document reflects the number of declared students available as of June 17, 2020 with ANY self-declared GPA. I have selected only states where we most actively recruit.



---

# Findings

### Rising Seniors

```{r echo=FALSE}
data_NR_SR <- data_NR %>% filter(Start == "Fall 2021")  
kable(data_NR_SR %>% arrange(desc(Number)))
```

### Rising Juniors

```{r echo=FALSE}
data_NR_JR <- data_NR %>% filter(Start == "Fall 2022")  


kable(data_NR_JR%>% arrange(desc(Number)))
```

### Rising Sophomores

```{r echo=FALSE}
data_NR_PH <- data_NR %>% filter(Start == "Fall 2023")  

kable(data_NR_PH%>% arrange(desc(Number)))
```

---

# Conclusions 

* The total cost for all 315 declared students would be $3,780.00.

* Cost for all 178 declared rising Seniors would be $2,136.00

* Cost for all 108 declared rising Juniors would be $1,296.00

* Cost for all 29 declared rising Sophomores would be $348.00

* If we select only the 302 students with a GPA of C+ or higher, the total cost would drop by $156.00

* It is important to understand that many of the Declared Students will already be in our database because we will have acquired them as leads (as long as we purchase from their county).
If leads have not converted to inquiries through one of our referral channels, 
we will not know they bacame inquiries unless we pay the declared student rate. The benefit to purchasing declared student names is that Admissions will know early on their high-level of interest.

* _Addendum_ June 24, 2020
Rachel, Tracy, and Chris met to discuss options in acquiring the NRCCUA Declared Students. Plan as follows:
  - Chris will pull historical conversion rates of historical out-of-state declared name purchase (~2016), The difference between the past and present purchases is that in 2016 there was potentially not the same out-of-state awareness. 
  - We plan to acquire the out-of-state names, which total 31, at a total cost of $372.00. The Office of Marketing and Branding will cover this cost. The purchase is tentatively scheduled for August. Chris will make Patricia Plourde aware of the decision and will ask how many names she expects by then. 
  - Because there is a tentative plan to purchase College Board leads in July, Chris will reach out to Pete Sison, CCB rep, to find out whether the June SAT happened and if names will even be available by August 1 in spite of the Covid-19 quarentine. 
  -

